---
title: "NOG"
subtitle: "Observing Plasticity in Fine and Course Motor Tasks"
format: revealjs
editor: visual
---

# Fine Motor Plasticity

-   Plasticity is the ability for the brain to learn new tasks

# Fine Motor Plasticity

-   Plasticity is the ability for the brain to learn new tasks

-   Famous examples include stroke patients relearning skills after consistent physical therapy

# Fine Motor Plasticity

-   Plasticity is the ability for the brain to learn new tasks

-   Famous examples include stroke patients relearning skills after consistent physical therapy Can we observe plasticity on Fine Motor Tasks?

-   Question: Can we use the Mirror Box to observe plasticity in the healthy brain?

# Fine Motor Plasticity

-   Plasticity is the ability for the brain to learn new tasks

-   Famous examples include stroke patients relearning skills after consistent physical therapy Can we observe plasticity on Fine Motor Tasks?

-   Question: Can we use the Mirror Box to observe plasticity in the healthy brain performing a fine motor task?

-   Null Hypothesis: If we can not observe plasticity with the mirror box, we should see the same average performance every time we try to draw shapes in the Mirror Box

## Mirror Box Results

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE)
```

```{r init, include=FALSE}
library(tidyverse)
library(googlesheets4)

gs4_auth(email = "sabudoff@gmail.com")

url = "https://docs.google.com/spreadsheets/d/1akxwgcooINQLVT4NIZWVJn9UD_0-_kmpf6lpOIWjmW0/edit?resourcekey#gid=1737655689"
df <- read_sheet(url, sheet = "Form Responses 1")
```

```{r data, echo=FALSE}
mirror_df <- df %>%
  filter(Task == "Mirror Box") %>%
  mutate(Attempt = `Mirror Box Attempt`,
         Shape = as.factor(`Mirror Box Shape`),
         `Time (s)` = `Mirror Box Time in Seconds`) %>%
  select(`Time (s)`, Attempt, Shape)

mirror_model <- lm(`Time (s)` ~ Attempt, data = mirror_df) 

intercept_mirror <- mirror_model$coefficients[1]
beta_mirror <- mirror_model$coefficients[2]
set.seed(18)

mirror_df %>%
  ggplot(aes(x=Attempt, y=`Time (s)`)) +
    geom_jitter(aes(color=Shape)) +
    ggtitle("Time to Trace Figure in Mirorr Box") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Mirror Box Result Distributions

```{r graph1, echo=FALSE}
set.seed(18)
mirror_df %>%
  mutate(Attempt=factor(Attempt)) %>%
  ggplot(aes(x=Attempt, y=`Time (s)`)) +
    geom_violin() +
    geom_jitter(aes(color=Shape)) +
    ggtitle("Time to Trace Figure in Mirorr Box") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Mirror Box Results Statistics

Time = `r beta_mirror`\*Attempt + `r intercept_mirror`

```{r stats1, echo=FALSE}
summary(mirror_model)
```

## Mirror Box Results Statistics

Time = `r beta_mirror`\*Attempt + `r intercept_mirror`

```{r graph2, echo=FALSE}
mirror_df %>%
  mutate(Prediction = intercept_mirror + beta_mirror*Attempt) %>%
  ggplot(aes(x=Attempt)) +
    geom_point(aes( y=`Time (s)`)) +
    geom_line(aes(y=Prediction)) +
    ggtitle("Learning Rate in Mirror Box") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Mirror Box Results Statistics

### Accounting for the shape being drawn

```{r stats2, echo=FALSE}
mirror_df <- mirror_df %>%
  mutate(Shape.1 = Shape == "Square",
         Shape.2 = Shape == "Heart",
         Shape.3 = Shape == "Star")
  

mirror_model2 <- lm(`Time (s)` ~ Attempt + Shape.1 + Shape.2 + Shape.3, data = mirror_df) 

intercept_mirror <- mirror_model2$coefficients[1]
beta_mirror_1 <- mirror_model2$coefficients[2]
beta_mirror_2 <- mirror_model2$coefficients[3]
beta_mirror_3 <- mirror_model2$coefficients[4]
beta_mirror_4 <- mirror_model2$coefficients[5]
```

Time = `r beta_mirror_1`\*Attempt + `r intercept_mirror` + Shape

```{r stats_rez2, echo=FALSE}
summary(mirror_model2)
```

## Mirror Box Results Statistics

### Accounting for the shape being drawn

Time = `r beta_mirror_1`\*Attempt + `r intercept_mirror` + Shape

```{r graph3, echo=FALSE}
mirror_df %>%
  mutate(Prediction = intercept_mirror + beta_mirror_1*Attempt + beta_mirror_2*Shape.1 + beta_mirror_3*Shape.2 + beta_mirror_4*Shape.3) %>%
  ggplot(aes(x=Attempt, group=Shape, color = Shape)) +
    geom_point(aes(y=`Time (s)`)) +
    geom_line(aes(y=Prediction)) +
    ggtitle("Learning Rate in Mirror Box Considering Shape") +
    theme_minimal() +
    theme(legend.position = 'None') +
    facet_wrap(~Shape)
```

## Mirror Box Results Statistics

### Accounting for the shape being drawn

Time = `r beta_mirror_1`\*Attempt + `r intercept_mirror` + Shape

```{r graph4, echo=FALSE}
mirror_df %>%
  mutate(Prediction = intercept_mirror + beta_mirror_1*Attempt + beta_mirror_2*Shape.1 + beta_mirror_3*Shape.2 + beta_mirror_4*Shape.3) %>%
  ggplot(aes(x=Attempt, group=Shape, color = Shape)) +
    geom_point(aes(y=`Time (s)`)) +
    geom_line(aes(y=Prediction)) +
    ggtitle("Learning Rate in Mirror Box Considering Shape") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Conclusion

So what did we learn?

Did we reject the null hypothesis (no change from trial to trial)?

Did the shape we were trying to trace matter? If so, what hypothesis can you propose based on the trends we saw?

# Coarse Motor Plasticity

-   Question: Can we use the cornhole and dizzy goggles to observe plasticity in the healthy brain performing a coarse motor task?

-   Null Hypothesis: If we can not observe plasticity with the dizzy goggles, we should see the same average score every time we try to get the beanbags in

## Cornhole Results


```{r data2ch, echo=FALSE}
ch_df <- df %>%
  filter(Task == "Cornhole") %>%
  mutate(Trial = `Cornhole Attempt`,
         Score = `Beanbag Scores`) %>%
  select(Score, Trial)


ch_model <- lm(Score ~ Trial, data = ch_df) 

intercept_ch <- ch_model$coefficients[1]
beta_ch <- ch_model$coefficients[2]
set.seed(18)

ch_df %>%
  ggplot(aes(x=Trial, y=Score)) +
    geom_jitter() +
    ggtitle("Score as a function of attempts") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Cornhole Result Distributions

```{r graph1ch, echo=FALSE}
set.seed(18)
ch_df %>%
  mutate(Trial = as.factor(Trial)) %>%
  ggplot(aes(x=Trial, y=Score)) +
    geom_violin() +
    geom_jitter() +
    ggtitle("Distribution of scores as a function of attempts") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Cornhole Results Statistics

Score = `r beta_ch`\*Trial + `r intercept_ch`

```{r stats1ch, echo=FALSE}
summary(ch_model)
```

## Cornhole Results Statistics

Score = `r beta_ch`\*Trial + `r intercept_ch`

```{r graph2ch, echo=FALSE}
ch_df %>%
  mutate(Prediction = intercept_ch + beta_ch*Trial) %>%
  ggplot(aes(x=Trial)) +
    geom_point(aes( y=Score)) +
    geom_line(aes(y=Prediction)) +
    ggtitle("Cornhole Learning Rate") +
    theme_minimal() +
    theme(legend.position = 'None')
```

## Conclusion

So what did we learn?

Did we reject the null hypothesis (no change from trial to trial)?

Comparing the fine motor task with the coarse motor task, do we think plasticity was more obvious in one case or another?